Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-06-26 doc/PRF2022/PRF_main.tex
updates

%
\begin{figure}
  \begin{center}
  \includegraphics[width=0.32\textwidth]{shear_0.png}
  \includegraphics[width=0.32\textwidth]{shear_1000.png}
  \includegraphics[width=0.32\textwidth]{shear_2000.png} 
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
\end{figure}
%
\begin{figure}
  \begin{center}
  \includegraphics[width=0.32\textwidth]{TG_0.png}
  \includegraphics[width=0.32\textwidth]{TG_2500.png}
  \includegraphics[width=0.32\textwidth]{TG_5000.png}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:TG_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(b) in a Taylor-Green flow when $V_0=0.1$ and $l=0.5$.}
\end{figure}
\subsection{Boundary condition (ii):  multilamellar configurations}

@@

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.21\textwidth]{shear_checker_0.png}
  \includegraphics[width=0.21\textwidth]{shear_checker_250.png}
  \includegraphics[width=0.21\textwidth]{shear_checker_500.png}
  \includegraphics[width=0.21\textwidth]{shear_checker_750.png} \\
%  \includegraphics[width=0.4\textwidth]{lambda_fig1.jpg}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
\end{figure}
%
\subsection{Boundary condition (iii): striated configurations}

@@

@@

>>>>

%
%\begin{figure}
%  \begin{center}
%  \includegraphics[width=0.32\textwidth]{shear_0.png}
%  \includegraphics[width=0.32\textwidth]{shear_1000.png}
%  \includegraphics[width=0.32\textwidth]{shear_2000.png} 
%  \end{center}
%  \vspace{-20pt}  
%  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
%\end{figure}
%
%\begin{figure}
%  \begin{center}
%  \includegraphics[width=0.32\textwidth]{TG_0.png}
%  \includegraphics[width=0.32\textwidth]{TG_2500.png}
%  \includegraphics[width=0.32\textwidth]{TG_5000.png}
%  \end{center}
%  \vspace{-20pt}  
%  \caption{\label{fig:TG_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(b) in a Taylor-Green flow when $V_0=0.1$ and $l=0.5$.}
%\end{figure}
\subsection{Boundary condition (ii):  multilamellar configurations}

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.22\textwidth]{MS_0.pdf}
  \includegraphics[width=0.22\textwidth]{MS_1.pdf}
  \includegraphics[width=0.22\textwidth]{MS_2.pdf} 
    \includegraphics[width=0.22\textwidth]{MS_3.pdf} 
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:MS_flow} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
\end{figure}

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.22\textwidth]{MTG_0.pdf}
  \includegraphics[width=0.22\textwidth]{MTG_1.pdf}
  \includegraphics[width=0.22\textwidth]{MTG_2.pdf} 
    \includegraphics[width=0.22\textwidth]{MTG_3.pdf} 
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:MTG_flow} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
\end{figure}

%\begin{figure}
%  \begin{center}
%  \includegraphics[width=0.21\textwidth]{shear_checker_0.png}
%  \includegraphics[width=0.21\textwidth]{shear_checker_250.png}
%  \includegraphics[width=0.21\textwidth]{shear_checker_500.png}
%  \includegraphics[width=0.21\textwidth]{shear_checker_750.png} \\
%%  \includegraphics[width=0.4\textwidth]{lambda_fig1.jpg}
%  \end{center}
%  \vspace{-20pt}  
%  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
%\end{figure}
%
\subsection{Boundary condition (iii): striated configurations}

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.22\textwidth]{CS_0.pdf}
  \includegraphics[width=0.22\textwidth]{CS_1.pdf}
  \includegraphics[width=0.22\textwidth]{CS_2.pdf} 
    \includegraphics[width=0.22\textwidth]{CS_3.pdf} 
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:CS_flow} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
\end{figure}

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.22\textwidth]{CTG_0.pdf}
  \includegraphics[width=0.22\textwidth]{CTG_1.pdf}
  \includegraphics[width=0.22\textwidth]{CTG_2.pdf} 
    \includegraphics[width=0.22\textwidth]{CTG_3.pdf} 
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:CTG_flow} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
\end{figure}
